\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans

### 2018-02-01 paper.tex
Fixed some grammar mistakes and added abstract

\begin{abstract} \small\baselineskip=9pt Increases in price and performance of automatic number plate recognition over the last two decades has led to  by law enforcement and urban traffic control. In this work we show how \end{abstract}

>>>>

\begin{abstract} \small\baselineskip=9pt In major cities, government agencies increasingly employ automatic number plate recognition (ANPR) technology in law enforcement and traffic control. In the region of Tyne and Wear (UK) the network of ANPR cameras is used to monitor travel times across sensitive roads. However, few works have explored the full potential of number plate scans for analysing individual and collective travel patterns. In this work we present a methodology for deriving trips from vehicle sightings at fixed camera locations. We illustrate the effect of parameters $\tau$ and $\Tau$ on trip discrimination and on the detection of implausible trips. To demonstrate the potential of trip data we apply \emph{k-means} clustering to trips identified from over 40 million plate scans recorded over 15 weekdays. Results show that whilst private and transit travel modes can begin to be inferred from the resulting clusters, further work needs to be put into developing a more consistent and integrated framework for trip identification in ANPR data.\end{abstract}
